### 2014-10-30 thesis/appendix/pt-rankeddist-summary.tex
All results are complete and tabulated nicely!

\vspace{15cm}
\caption{}

@@

 & \multicolumn{20}{c|}{Ranked Distance $c$ - Discretisation} \\ \hline
k & \multicolumn{ 2}{l|}{0.1} & \multicolumn{ 2}{l|}{0.2} & \multicolumn{ 2}{l|}{0.3} & \multicolumn{ 2}{l|}{0.4} & \multicolumn{ 2}{l|}{0.5} & \multicolumn{ 2}{l|}{0.6} & \multicolumn{ 2}{l|}{0.7} & \multicolumn{ 2}{l|}{0.8} & \multicolumn{ 2}{l|}{0.9} & \multicolumn{ 2}{l|}{1} \\ \hline
 & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} \\ \hline

@@

 & \multicolumn{20}{c|}{Ranked Distance $c$ - Discretisation} \\ \hline
k & \multicolumn{ 2}{l|}{0.1} & \multicolumn{ 2}{l|}{0.2} & \multicolumn{ 2}{l|}{0.3} & \multicolumn{ 2}{l|}{0.4} & \multicolumn{ 2}{l|}{0.5} & \multicolumn{ 2}{l|}{0.6} & \multicolumn{ 2}{l|}{0.7} & \multicolumn{ 2}{l|}{0.8} & \multicolumn{ 2}{l|}{0.9} & \multicolumn{ 2}{l|}{1} \\ \hline
 & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} \\ \hline

@@

 & \multicolumn{20}{c|}{Ranked Distance $c$ - No Discretisation} \\ \hline
k & \multicolumn{ 2}{l|}{0.1} & \multicolumn{ 2}{l|}{0.2} & \multicolumn{ 2}{l|}{0.3} & \multicolumn{ 2}{l|}{0.4} & \multicolumn{ 2}{l|}{0.5} & \multicolumn{ 2}{l|}{0.6} & \multicolumn{ 2}{l|}{0.7} & \multicolumn{ 2}{l|}{0.8} & \multicolumn{ 2}{l|}{0.9} & \multicolumn{ 2}{l|}{1} \\ \hline
 & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{Acc} & \multicolumn{ 1}{l|}{+/-} \\ \hline

@@

 & \multicolumn{20}{c|}{Ranked Distance $c$ - No Discretisation} \\ \hline
k & \multicolumn{ 2}{l|}{0.1} & \multicolumn{ 2}{l|}{0.2} & \multicolumn{ 2}{l|}{0.3} & \multicolumn{ 2}{l|}{0.4} & \multicolumn{ 2}{l|}{0.5} & \multicolumn{ 2}{l|}{0.6} & \multicolumn{ 2}{l|}{0.7} & \multicolumn{ 2}{l|}{0.8} & \multicolumn{ 2}{l|}{0.9} & \multicolumn{ 2}{l|}{1} \\ \hline
 & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} & \multicolumn{ 1}{l|}{AUC} & \multicolumn{ 1}{l|}{+/-} \\ \hline

>>>>

\vspace{15.7cm}
\caption{Results for the $k$-NN classifier with our proposed Ranked Distance approach on the general hospital data set with and without discretisation, for varying numbers of numbers $k$ and decay constant $c$.}

@@

 & \multicolumn{20}{c|}{Decay constant $c$ - Discretisation} \\ \hline
 & \multicolumn{ 2}{c|}{0.1} & \multicolumn{ 2}{c|}{0.2} & \multicolumn{ 2}{c|}{0.3} & \multicolumn{ 2}{c|}{0.4} & \multicolumn{ 2}{c|}{0.5} & \multicolumn{ 2}{c|}{0.6} & \multicolumn{ 2}{c|}{0.7} & \multicolumn{ 2}{c|}{0.8} & \multicolumn{ 2}{c|}{0.9} & \multicolumn{ 2}{c|}{1} \\
k & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- \\ \hline

@@

 & \multicolumn{20}{c|}{Decay constant $c$ - Discretisation} \\ \hline
 & \multicolumn{ 2}{c|}{0.1} & \multicolumn{ 2}{c|}{0.2} & \multicolumn{ 2}{c|}{0.3} & \multicolumn{ 2}{c|}{0.4} & \multicolumn{ 2}{c|}{0.5} & \multicolumn{ 2}{c|}{0.6} & \multicolumn{ 2}{c|}{0.7} & \multicolumn{ 2}{c|}{0.8} & \multicolumn{ 2}{c|}{0.9} & \multicolumn{ 2}{c|}{1} \\
k & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- \\ \hline

@@

 & \multicolumn{20}{c|}{Decay constant $c$ - No Discretisation} \\ \hline
 & \multicolumn{ 2}{c|}{0.1} & \multicolumn{ 2}{c|}{0.2} & \multicolumn{ 2}{c|}{0.3} & \multicolumn{ 2}{c|}{0.4} & \multicolumn{ 2}{c|}{0.5} & \multicolumn{ 2}{c|}{0.6} & \multicolumn{ 2}{c|}{0.7} & \multicolumn{ 2}{c|}{0.8} & \multicolumn{ 2}{c|}{0.9} & \multicolumn{ 2}{c|}{1} \\
k & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- & Acc & +/- \\ \hline

@@

 & \multicolumn{20}{c|}{Decay constant $c$ - Discretisation} \\ \hline
 & \multicolumn{ 2}{c|}{0.1} & \multicolumn{ 2}{c|}{0.2} & \multicolumn{ 2}{c|}{0.3} & \multicolumn{ 2}{c|}{0.4} & \multicolumn{ 2}{c|}{0.5} & \multicolumn{ 2}{c|}{0.6} & \multicolumn{ 2}{c|}{0.7} & \multicolumn{ 2}{c|}{0.8} & \multicolumn{ 2}{c|}{0.9} & \multicolumn{ 2}{c|}{1} \\
k & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- & AUC & +/- \\ \hline
